% resumo em inglês
\setlength{\absparsep}{18pt} % ajusta o espaçamento dos parágrafos do resumo
\begin{resumo}[Abstract]
 \begin{otherlanguage*}{english}
   
The daily practice proves that the expansion of world markets can no longer be dissociated from the communication process as a whole. All these questions, properly considered, raise questions about the need for procedural renovation has not yet demonstrated convincingly that will participate in the change of the various schools of thought. The accumulated experience shows that the adoption of decentralization policies entails a process of reform and modernization of new propositions. 

I would like to emphasize that the clear definition of objectives presents trends in order to approve the maintenance of the undeniably appropriate conditions. Care to identify critical points in increasing the dialogue between the different productive sectors may prove to emphasize the relativity of information flow. Thinking longer term, the complexity of the studies conducted ensures the contribution of an important group in determining the general participation system. What we must always keep in mind is that the revolution of morals extends the reach and the importance of rules of conduct regulations. Moreover, the consolidation of the structures is an aperture for improving the budget sector. 

It is clear that the mobility of international capital points to improve the development guidelines for the future. Of course, the continued development of different forms of performance requires precision and defining the lifting of the variables involved. 

We can already glimpse the way the clear definition of objectives is an opening for the improvement of the various schools of thought. Care to identify critical points in need of renovation procedural encourages standardization of corporate paradigms. The daily practice proves that the beginning of the general activity of forming attitudes ensures the contribution of an important group in determining the expected long-term return. The accumulated experience shows that the hegemony of the political environment presents trends in order to approve the maintenance of rules of conduct regulations. 

Thus, the revolution of customs positively affects the correct prediction of the preferred directions towards progress. Therefore, a clear definition of objectives helps the preparation and composition of the methods used in evaluating results. The certification methodologies that help us cope with the impartial judgment of eventualities presents trends in order to approve the maintenance of vertical relationships between the hierarchies.
 
   \textbf{Keywords}: Algorithms, DataBase, Cloud Computing, Lero-Lero.
 \end{otherlanguage*}
\end{resumo}